%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parindent}{4em}
\setlength{\parskip}{1em}

\documentclass[]{deedy-resume-openfont}

\usepackage[numbers]{natbib}
\usepackage{ragged2e}
\usepackage{acronym} % \ac[p], \acl[p], \acs[p], \acf[p]

% Acronyms
% --------
\acrodef{CRDT}[CRDT]{Conflict-free Replicated Data Type}
\acrodefplural{CRDT}[CRDTs]{Conflict-free Replicated Data Types}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     CONTACT INFORMATION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\contact

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Matthieu}{NICOLAS}{ \href{mailto:matthieu.nicolas@inria.fr}{matthieu.nicolas@inria.fr} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Career}

\runsubsection{PhD Student}
\descript{| INRIA, COAST TEAM}
\location{October 2017 - Today | Nancy, France}
\sectionsep

\hfill\begin{minipage}{\dimexpr\textwidth-0.5cm}
\descript{EFFICIENT (RE)NAMING IN CONFLICT-FREE REPLICATED DATA TYPES}

\acp{CRDT} are data structures behaving as traditional ones, like \emph{Set} or \emph{Sequence} data structures, but designed for a distributed usage.
They are used in order to build large scale distributed systems adopting the optimistic replication model known as eventual consistency to replicate data among nodes.
With this model, each node owning a copy of the data can edit it without any kind of coordination with other nodes.
They then propagate the updates to others.
The specification of \acp{CRDT} ensures that concurrent updates are resolved deterministically and that replicas eventually converge after observing all of them.
\\
To achieve convergence, \acp{CRDT} proposed in the literature mostly rely on identifiers to reference updated elements.
According to the kind of \ac{CRDT}, identifiers have to comply to several constraints (unicity, belonging to a dense set...).
\\
Because of these constraints, the identifiers size is often not bounded.
The size of metadata attached to each element increases with the number of updates.
It thus exceeds more and more the size of data itself, decreasing the efficiency of the data structure over time.
\\
The goal of this PhD is to address this issue by
\begin{tightemize}
  \item Proposing more efficient specifications of identifiers according to their set of constraints,
  \item Proposing mechanisms to rename identifiers to reduce their size.
\end{tightemize}
\sectionsep
\end{minipage}

\runsubsection{Research \& Development Software Engineer}
\descript{| INRIA, COAST TEAM}
\location{September 2014 – September 2017 | Nancy, France}
\sectionsep

\hfill\begin{minipage}{\dimexpr\textwidth-0.5cm}
\descript{PROJECT OPENPAAS::NG}
The goal of this project is to design an open-source entreprise social network providing a suite of
peer-to-peer collaborative office applications.
The aim is to offer a reliable and free alternative to existing solutions such as Google Apps.
This project is a joint work with the team DaSciM (Data Science and Mining) from the
computer science laboratory from the Ecole Polytechnique, Linagora, XWiki SAS and Nexedi.
\\
In this project, the COAST team works on topics such as the interorganisational federation of
peer-to-peer systems and the securing of communications in this kind of collaboration.
Furthermore, the team provides its expertise
on eventually consistent data replication mechanisms in distributed systems.
\\
In order to validate them, these works have been integrated in \href{https://www.coedit.re}{\customboldlink{MUTE}},
peer-to-peer web based real-time collaboration editor.
\begin{tightemize}
\item Maintaining of LogootSplit implementation
\item Study of the literature on Conflict-free Replicated Data Types and of their use cases.
\item Development and integration of an anti-entropy mechanism
\end{tightemize}
\sectionsep
\end{minipage}

\section{EDUCATION}

\runsubsection{Master Degree in Computer Science}
\descript{}
\location{Engineering degree in Computer Science at TELECOM Nancy}
\location{September 2011 – August 2014 | Nancy, France}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{document}
